Differentiable Neural Computers

### 2018-05-14 Presentation/Presentation.tex
less math

%----------------------------------------------------------------------------
% LoCo
%----------------------------------------------------------------------------
\setbeamertemplate{frametitle}[default][center]
\newcommand{\xx}{\pmb{\raisebox{-1.5pt}{$\mathcal{X}$}}}
\newcommand{\hh}{\pmb{h}}
\newcommand{\ii}{\pmb{i}}
\newcommand{\oo}{\pmb{o}}
\newcommand{\ff}{\pmb{f}}
\newcommand{\Ss}{\pmb{s}}
\newcommand{\bb}{\pmb{b}}

@@

	\pause
	\begin{itemize}
	\item Inspired by biological memory
	\item Reimaging of classical concepts of computation
	\item Extension of NTMs
	\begin{itemize}
		\item End-to-end differentiable
		\item Auto-associative memory
		\item Turing complete
		\item[+] Stronger memory management
	\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Controller: Overview}
	A deep \alert{long short-term memory network} receiving input:
	\[
	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R] \tag{\text{\alert{timestep t}}}
	\]
	and producing output:
	\[
	(\pmb{\upsilon}_T,\pmb{\xi}_T)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta) \tag{\text{\alert{entire sequence}}}
	\]
	where $\mathcal{N}$ a set of state equations and $\vartheta$ their trainable parameters.
\end{frame}

\begin{frame}{Controller: State Equations}
	A more detailed look into $\mathcal{N}$.\\

%	\pause
%	\begin{equation*}
%	\begin{rcases}
%  	\text{\alert{Input}} &: [\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]\\
%  	\text{\alert{Output}} &: \hh_t^l\\
%	\end{rcases}
%	\text{(\alert{Layer \alert{l} at time \alert{t}})}
%	\end{equation*}

	\pause		
	\underline{\alert{LSTM layer equations}}

	\alert{Input}: $[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]$ \\
	\alert{Output}: $\hh_t^l$
	\pause
	\begin{align}
	\ii_t^l &= \zeta_i([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]) \tag{\alert{input gate}}\\
	\ff_t^l &= \zeta_f([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}])	\tag{\alert{forget gate}}\\
	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^l\zeta_s([\xx_t;\hh_{t_1}^l;\hh_t^{l-1}]) \tag{\alert{state update}}\\
	\oo_t^l &= \zeta_o([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}])	\tag{\alert{output gate}}\\
	\hh_t^l &= \oo_t^l\zeta_h(\Ss_t^l)		\tag{\alert{hidden layer}}
	\end{align}
%	\nonumber \\ 
%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
%	\end{align}
%	\begin{align}
%	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
%	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
%	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
%	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
%	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
%	\nonumber \\ 
%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
%	\end{align}
\end{frame}

\begin{frame}{Controller: Signal-Flow (1/2)}
	\alert{Single LSTM layer}
	\begin{figure}
	\begin{tikzpicture}[scale=0.5]
		%-------------------------------------------------------------------------------
		% LSTM
		%-------------------------------------------------------------------------------
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{mDarkTeal}{$;$}};

@@

		% core nodes
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{black}{$;$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
			at (9,6) {\large\textcolor{black}{$\Ss_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
			at (9,4) {\textcolor{black}{$\times$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (f) 
			at (9,2) {\large\textcolor{black}{$\ff_t^l$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (i) 
			at (6,8) {\large\textcolor{black}{$\ii_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
			at (6,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (id) 
			at (4,8) {\textcolor{black}{$\zeta_i$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (sd) 
			at  (4,6) {\small\textcolor{black}{$\zeta_s$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
			at (16,10) {\large\textcolor{black}{$\oo_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
			at (16,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (hd) 
			at (12,6) {\small\textcolor{black}{$\zeta_h$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (odd) 
			at (4,10) {\small\textcolor{black}{$\zeta_o$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (fd) 
			at (4,2) {\small\textcolor{black}{$\zeta_f$}};
		% recurrency
		\draw (f) edge[thick] (fd);
		\draw[thick] (fd) -| (2,6);
		\draw[thick] (2,6) |- (odd);
		\draw (odd) edge[->,thick] (o);
		\draw[thick] (2,6) |- (id);
		\draw (id) edge[thick] (i);
		% gates
		\draw (o) edge[->, thick] (ox);
		\draw (i) edge[->, thick] (ix);
		\draw (s) edge[->,bend right=45, thick, densely dotted, gray!90] (fx);
		\draw (s) edge[<-,bend left=45, thick] (fx);
		\draw (f) edge[->, thick] (fx);
		% forward
		\draw (-2,4)[->,thick] -| (conc);
		\draw(-2,6) edge[thick,->] (conc);
		\draw (0,6) edge[thick] (sd);
		\draw (sd) edge[->, thick] (ix);
		\draw (ix) edge[->, thick] (s);
		\draw (s) edge[thick] (hd);
		\draw (hd) edge[->, thick] (ox);
		\draw (ox) edge[->, thick] (20,6);

		% labels
		\node[label=below:$\textcolor{white}{\hh_t^{l-1}}$] (ht1) at (-1,4) {};
		\node[label=above:$\textcolor{white}{\xx_t}$] (x) at (-1,6) {};
		\node[label=above:$\textcolor{white}{\hh_t^l}$] (ht) at (19.5,6) {};
		\node[label=above:$\textcolor{white}{\hh_{t-1}^l}$] (x) at (9,12) {};
		\end{tikzpicture}
		\end{figure}
\end{frame}

\begin{frame}{Controller: Signal-Flow (2/2)}
	\alert{LSTM Network} (multiple layers)
	\begin{figure}
	\begin{tikzpicture}[scale=1]
	\tikzset{miniLSTM/.style={draw=black, fill=white, minimum width=20pt, minimum height=10pt, thick}}
	\tikzset{split/.style={circle, draw=black,inner sep=0pt, minimum size = 3mm, fill=white}}
		\node (dummy_node) at (0,0) {};
		\foreach \name/\x in {x1/2, x2/4, x3/6, xd/8, xL/10} {\node[inner sep=0] (\name) at (\x,0) {};}
		\foreach \name/\x in {h1/3, h2/5, h3/7, hL/10} {\node[inner sep=0] (\name) at (\x, -2) {};}
		\foreach \name/\x in {s1/5, s2/7, sL/10} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
		\foreach \name/\x/\tag in {L1/2/$LSTM_1$, L2/4/$LSTM_2$, L3/6/$LSTM_3$, LL/10/$LSTM_L$} 
		{\node[miniLSTM] (\name) at (\x,-2) {\textcolor{black}{\tiny\tag}};}
		\node (Ld) at (8,-2) {$\dots$};
		\node (sd) at (8,-3) {$\dots$};
		\draw (dummy_node) -| (LL);
		\draw (L1) edge[->,thick] (L2);
		\draw (L2) edge[->,thick] (L3);
		\draw (L3) edge[->,thick] (Ld);
		\draw (Ld) edge[->,thick] (LL);
		\draw[->,thick] (x1) edge (L1.north);
		\draw[->,thick] (x2) edge (L2.north);
		\draw[->,thick] (x3) edge (L3.north);
		\draw[->,thick] (xL) edge (LL.north);
		\draw[->,thick] (xd) edge (Ld.north);
		%\draw[->,thick] (1,0) |- (s0);
		\draw[->,thick] (h1) |- (s1);
		\draw[->,thick] (h2) edge (s1);
		\draw[->,thick] (h3) edge (s2);
		\draw[->,thick] (s1) edge (s2);
		\draw[->,thick] (s2) edge (sd);
		\draw[->,thick] (sd) edge (sL);
		\draw[->,thick] (LL) edge (sL);		
		\draw[->,thick] (sL) edge (10, -5);
		% labels
		\node[label=above right :$\scriptsize\textcolor{white}{\xx_t}$] (xt) at (0,0) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^1}$] (xt) at (3,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^2}$] (xt) at (5,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^3}$] (xt) at (7,-2) {};
		\node[label=below :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
		\node[label=left :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2;\dots;\hh_t^L]}$] (xt) at (10,-5) {};
	\end{tikzpicture}
	\end{figure}
\end{frame}

@@

\begin{frame}{Memory Adressing: Temporal Linking}
	\alert{Free gates} $\pmb{\phi}_t^i \in [0,1]^W$\\

	\alert{Memory retention}
	\begin{align*}
	\pmb{\psi}_t = \prod\limits_{i=1}^R (\pmb{1} - \pmb{\phi}_t^iw_{t-1}^{r,i}) \\
	\end{align*}

	\pause
	\alert{Usage tracking}
	\begin{align*}
	u_t = (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w + \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t\\
	\end{align*}

	\pause
	\alert{Allocation vector} $\pmb{a}_t$ given by normalizing and sorting $\pmb{u}_t$
\end{frame}

@@

\begin{frame}{Conclusion}
	\alert{Takeaway}\\
	We can automatically infer simple functions over complex data structures, in the form of \alert{probability distributions} just by using examples.\\

@@

>>>>

%----------------------------------------------------------------------------
% LoCo
%----------------------------------------------------------------------------
\setbeamertemplate{frametitle}[default][center]
\newcommand{\xx}{\pmb{\raisebox{-1.5pt}{$\mathcal{X}$}}}
\newcommand{\hh}{\pmb{h}}
\newcommand{\ii}{\pmb{i}}
\newcommand{\oo}{\pmb{o}}
\newcommand{\ff}{\pmb{f}}
\newcommand{\Ss}{\pmb{s}}
\newcommand{\Cc}{\pmb{c}}
\newcommand{\bb}{\pmb{b}}

@@

	\pause
	\begin{itemize}
	\item Functional replication of biological memory
	\item Reimaging of classical concepts of computation
	\item Extension of NTMs
	\begin{itemize}
		\item End-to-end differentiable
		\item Auto-associative memory
		\item Turing complete
		\item[+] Computationally efficient memory management
	\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Controller: Overview}
	A deep \alert{long short-term memory network} receiving input:
	\[
	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R] \tag{\text{\alert{timestep t}}}
	\]
	and producing output:
	\[
	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_t];\vartheta) \tag{\text{\alert{entire sequence}}}
	\]
	where \alert{$\mathcal{N}$} a set of state equations and \alert{$\vartheta$} their trainable parameters.
\end{frame}

\begin{frame}{LSTM: Overview}
	\alert{LSTM Network}\\
	Multiple stacked LSTM units.

	\alert{LSTM Unit}\\
	A RNN that has an intrinsic memory \alert{cell} $\Cc_t^l$ and three \alert{gates}.

	\pause
	\begin{enumerate}
	\item \alert{Input gate} $\ii_t^l$ %regulating flow to the memory cell
	\item \alert{Forget gate} $\ff_t^l$ %selectively erasing memory cell contents
	\item \alert{Output gate} $\oo_t^l$ %regulating flow from the memory cell to the output
	\end{enumerate}

\end{frame}

\begin{frame}{LSTM: Signal-Flow (1/2)}
	\alert{LSTM Unit} (single layer)
	\begin{itemize}
	\item	\alert{Input}: $[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]$\\
	\item	\alert{Output}: $\hh_t^l$\\	
	\end{itemize}

	\pause
	\vspace{-10pt}
	\begin{figure}
	\begin{tikzpicture}[scale=0.45]
		%-------------------------------------------------------------------------------
		% LSTM
		%-------------------------------------------------------------------------------
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{mDarkTeal}{$;$}};

@@

		% core nodes
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{black}{$;$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
			at (9,6) {\large\textcolor{black}{$\Cc_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
			at (9,4) {\textcolor{black}{$\times$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (f) 
			at (9,2) {\large\textcolor{black}{$\ff_t^l$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (i) 
			at (6,8) {\large\textcolor{black}{$\ii_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
			at (6,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (id) 
			at (4,8) {\textcolor{black}{$\zeta_i$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (sd) 
			at  (4,6) {\small\textcolor{black}{$\zeta_c$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
			at (16,10) {\large\textcolor{black}{$\oo_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
			at (16,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (hd) 
			at (12,6) {\small\textcolor{black}{$\zeta_h$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (odd) 
			at (4,10) {\small\textcolor{black}{$\zeta_o$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (fd) 
			at (4,2) {\small\textcolor{black}{$\zeta_f$}};
		% recurrency
		\draw (f) edge[thick] (fd);
		\draw[thick] (fd) -| (2,6);
		\draw[thick] (2,6) |- (odd);
		\draw (odd) edge[->,thick] (o);
		\draw[thick] (2,6) |- (id);
		\draw (id) edge[thick] (i);
		% gates
		\draw (o) edge[->, thick] (ox);
		\draw (i) edge[->, thick] (ix);
		\draw (s) edge[->,bend right=45, thick, densely dotted, gray!90] (fx);
		\draw (s) edge[<-,bend left=45, thick] (fx);
		\draw (f) edge[->, thick] (fx);
		% forward
		\draw (-2,4)[->,thick] -| (conc);
		\draw(-2,6) edge[thick,->] (conc);
		\draw (0,6) edge[thick] (sd);
		\draw (sd) edge[->, thick] (ix);
		\draw (ix) edge[->, thick] (s);
		\draw (s) edge[thick] (hd);
		\draw (hd) edge[->, thick] (ox);
		\draw (ox) edge[->, thick] (20,6);

		% labels
%		\node[label=above:$\textcolor{white}{\mathcal{I}}$] (we) at (1,6) {};		
		\node[label=below:$\textcolor{white}{\hh_t^{l-1}}$] (ht1) at (-1,4) {};
		\node[label=above:$\textcolor{white}{\xx_t}$] (x) at (-1,6) {};
		\node[label=above:$\textcolor{white}{\hh_t^l}$] (ht) at (19.5,6) {};
		\node[label=above:$\textcolor{white}{\hh_{t-1}^l}$] (x) at (9,12) {};
		\end{tikzpicture}
		\end{figure}
\end{frame}

\begin{frame}{Controller: Signal-Flow (2/2)}
	\alert{LSTM Network} (multiple layers)
	\begin{itemize}
	\item	\alert{Input}: $\xx_t$\\
	\item	\alert{Output}: $[\hh_t^1;\hh_t^2;\dots\hh_t^L]$\\	
	\end{itemize}
	\pause
	\begin{figure}
	\begin{tikzpicture}[scale=1]
	\tikzset{miniLSTM/.style={draw=black, fill=white, minimum width=20pt, minimum height=10pt, thick}}
	\tikzset{split/.style={circle, draw=black,inner sep=0pt, minimum size = 3mm, fill=white}}
		\node (dummy_node) at (1,0) {};
		\foreach \name/\x in {x1/2, x2/4, x3/6, xd/8, xL/10} {\node[inner sep=0] (\name) at (\x,0) {};}
		\foreach \name/\x in {h1/3, h2/5, h3/7, hL/10} {\node[inner sep=0] (\name) at (\x, -2) {};}
		\foreach \name/\x in {s1/5, s2/7, sL/11} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
		\foreach \name/\x/\tag in {L1/2/$LSTM_1$, L2/4/$LSTM_2$, L3/6/$LSTM_3$, LL/10/$LSTM_L$} 
		{\node[miniLSTM] (\name) at (\x,-2) {\textcolor{black}{\tiny\tag}};}
		\node (Ld) at (8,-2) {$\dots$};
		\node (sd) at (9,-3) {$\dots$};
		\draw (dummy_node) -| (LL);
		\draw (L1) edge[->,thick] (L2);
		\draw (L2) edge[->,thick] (L3);
		\draw (L3) edge[->,thick] (Ld);
		\draw (Ld) edge[->,thick] (LL);
		\draw[->,thick] (x1) edge (L1.north);
		\draw[->,thick] (x2) edge (L2.north);
		\draw[->,thick] (x3) edge (L3.north);
		\draw[->,thick] (xL) edge (LL.north);
		\draw[->,thick] (xd) edge (Ld.north);
		%\draw[->,thick] (1,0) |- (s0);
		\draw[->,thick] (h1) |- (s1);
		\draw[->,thick] (h2) edge (s1);
		\draw[->,thick] (h3) edge (s2);
		\draw[->,thick] (s1) edge (s2);
		\draw[->,thick] (s2) edge (sd);
		\draw[->,thick] (sd) edge (sL);
		\draw[->,thick] (LL) -| (sL);		
		\draw[->,thick] (sL) edge (11, -4);
		\draw (L1.east) [->, densely dotted, thick, gray!90] .. controls +(0.6,-0.8) and +(-0.6,-0.8) .. (L1.south);
		\draw (L2.east) [->, densely dotted, thick, gray!90] .. controls +(0.6,-0.8) and +(-0.6,-0.8) .. (L2.south);
		\draw (LL.east) [->, densely dotted, thick, gray!90] .. controls +(0.6,-0.8) and +(-0.6,-0.8) .. (LL.south);
		% labels
		\node[label=above right :$\scriptsize\textcolor{white}{\xx_t}$] (xt) at (1,0) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^1}$] (xt) at (3,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^2}$] (xt) at (5,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^3}$] (xt) at (7,-2) {};
		\node[label=below :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
		\node[label=left :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2;\dots;\hh_t^L]}$] (xt) at (11,-4) {};
	\end{tikzpicture}
	\end{figure}
\end{frame}

@@

\begin{frame}{Memory Adressing: Temporal Linking}

\end{frame}

@@

\begin{frame}{Conclusion}
	\alert{Takeaway}\\
	We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\

@@

\begin{frame}{LSTM: State Equations}

	\begin{align}
	\ii_t^l &= \zeta_i(\mathcal{I}) \tag{\alert{input gate}}\\
	\ff_t^l &= \zeta_f(\mathcal{I})	\tag{\alert{forget gate}}\\
	\Cc_t^l &= \ff_t^l\Cc_{t-1}^l + \ii_t^l\zeta_c(\mathcal{I}) \tag{\alert{memory cell}}\\
	\oo_t^l &= \zeta_o(\mathcal{I})	\tag{\alert{output gate}}\\
	\hh_t^l &= \oo_t^l\zeta_h(\Cc_t^l)		\tag{\alert{hidden layer}}
	\end{align}
%	\nonumber \\ 
%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
%	\end{align}
%	\begin{align}
%	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
%	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
%	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
%	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
%	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
%	\nonumber \\ 
%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
%	\end{align}
\end{frame}
